---
title: "Homework 5"
author: "David Rodden"
date: "March 25, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("Lock5withR", lib.loc="~/R/win-library/3.3")
```

###6.188
```{r}
total.male = length(which(ICUAdmissions$Sex == 0))
total.female = length(which(ICUAdmissions$Sex == 1))
dead.male = length(subset(ICUAdmissions, Sex == 0 & Status == 1))
dead.female = length(subset(ICUAdmissions, Sex == 1 & Status == 1))
deadProp.male = dead.male / total.male
deadProp.female = dead.female / total.female
deadProp.difference = deadProp.male - deadProp.female
```
To ensure that the sample size is large enough in each group, we check that $n_1p_1, n_1(1-p_1), n_2p_2, n_2(1 - p_2) \geq 10$.
```{r}
male.test1 = total.male * deadProp.male; male.test1
male.test2 = total.male * (1 - deadProp.male); male.test2
female.test1 = total.female * deadProp.female; female.test1
female.test2 = total.female * (1 - deadProp.female); female.test2
```
Since all are above, 10, we know that the sample size is large enough in each group.
```{r}
deadProp.se = sqrt(
    (deadProp.male * (1 - deadProp.male) / total.male) + 
    (deadProp.female * (1 - deadProp.female) / total.female))
z.star = qnorm(.955)
confidence.lower = deadProp.difference - z.star * deadProp.se; confidence.lower
confidence.upper = deadProp.difference + z.star * deadProp.se; confidence.upper
```

The 95% confidence interval for the difference in the proportion who die between males and females is between `r confidence.lower` and `r confidence.upper`.

###6.204
*(a)*

$H_0: p_t = p_p; H_a: p_t > p_t$
```{r}
size.thc = 79; size.proch = 78
effective.thc = 36; effective.proch = 16
thc.test = prop.test(c(effective.thc, effective.proch), c(size.thc, size.proch),
                     alternative = "greater")
p.value = thc.test$p.value
```
Since the p-value is $`r p.value`$, which is less than 0.01 per the significance level, we reject the null hypothesis in favor of the alternative hypothesis.

*(b)*

It is important that these data come from a well-designed experiment so that the results are clear and so that they cannot be misconstrued.

###6.248

```{r}
total.male = subset(NutritionStudy, Sex == "Male")$Fiber
total.female = subset(NutritionStudy, Sex == "Female")$Fiber
size.male = length(total.male)
size.female = length(total.female)
fiber.male = mean(total.male)
fiber.female = mean(total.female)
fiber.difference = fiber.male - fiber.female
fiber.se = sqrt(
  (sd(total.male)^2/size.male) + 
    (sd(total.female)^2/size.female));fiber.se
fiber.df = if(size.male > size.female)  size.male - 1 else size.female - 1
t.star = qt(.955, fiber.df);t.star
confidence.lower = fiber.difference - t.star * fiber.se
confidence.upper = fiber.difference + t.star * fiber.se
```
The 95% confidence interval for the difference in number of grams of fiber eaten in a day between males and females is between `r confidence.lower` and `r confidence.upper`.
No difference between males and females is a plausible option for the population difference in number of grams of fiber eaten because 0 falls within the 95% confidence interval displayed above.

###2.290

Since the group of students are being used for two different tests, this is paired data.

```{r}
size.total = length(QuizPulse10$Student)
mean.lecture = mean(QuizPulse10$Lecture)
mean.quiz = mean(QuizPulse10$Quiz)
sd.lecture = sd(QuizPulse10$Lecture)
sd.quiz = sd(QuizPulse10$Quiz)
mean.difference = mean.lecture - mean.quiz
sd.difference = sd.lecture - sd.quiz
t.star = qt(.955, size.total - 1)
confidence.lower = mean.difference - t.star * sd.difference / sqrt(size.total)
confidence.upper = mean.difference + t.star * sd.difference / sqrt(size.total)
```
The 95% confidence interval for the difference in mean pulse rate between students in a class lecture and taking a quiz is between `r confidence.lower` and `r confidence.upper`.

###C.14

*(a)*

$H_0: p_s = p_{ns}; H_a: p_s < p_{ns}$
```{r}
prop.test(length(which(NutritionStudy$Smoke == "Yes")), length(NutritionStudy$Smoke), conf.level = 0.95)
```

*(b)*
```{r}
t.test(NutritionStudy$Fiber)
```

*(c)*


*(d)*

$H_0: p_m = p_f; H_a: p_m > p_f$
```{r}
pop.smoker = subset(NutritionStudy, Smoke == "Yes")
pop.test = prop.test(length(which(pop.smoker$Sex == "Male")), length(pop.smoker$Sex)
          , alternative = "less"); pop.test
p.value = pop.test$p.value
```
Considering the p-value is $`r p.value`$.

*(e)*

$H_0: \mu_m = \mu_f; H_a: \mu_m \neq \mu_f$
```{r}
chol.male = subset(NutritionStudy, Sex == "Male")$Cholesterol
chol.female = subset(NutritionStudy, Sex == "Female")$Cholesterol
chol.test = t.test(chol.male, chol.female, alternative = "two.sided")
chol.test
p.value = chol.test$p.value; p.value
```
According to our t-test, it can be seen that the p-value is $`r p.value`$, which is very small ($< 0.01$), and so the null hypothesis should be rejected in favor of the alternative hypothesis that the difference in mean cholesterol levels by gender is not 0.

*(f)*

$H_0: \mu_s = \mu_{ns}; H_a: \mu_s \neq \mu_{ns}$
```{r}
bp.smoker = subset(NutritionStudy, Smoke = "Yes")$BetaPlasma
bp.nonsmoker = subset(NutritionStudy, Smoke = "No")$BetaPlasma
bp.test = t.test(bp.smoker, bp.nonsmoker, alternative = "two.sided")
bp.test
p.value = bp.test$p.value; p.value
```
According to our t-test, it can be seen that the p-value is `r p.value`, which is very large, and so the alternative hypothesis is rejected and the null hypothesis that there is no difference in mean level of beta carotene in the blood between smokers & non-smokers is accepted.


###C.72

$H_0: \mu_c = \mu_s; H_a: \mu_c \neq \mu_s$
```{r}
commute.carbon = subset(BikeCommute, Bike == "Carbon")$Minutes
commute.steel = subset(BikeCommute, Bike == "Steel")$Minutes
commute.test = t.test(commute.steel, commute.carbon, alternative = "two.sided")
commute.test
p.value = commute.test$p.value
```
Since the p-value generated by the t-test is `r p.value`, we can see that it is quite large ($> 0.1$), and hence we do not accept the alternative hypothesis.