---
title: "Statistics Homework 7"
author: "David Rodden"
date: "April 20, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("Lock5withR", lib.loc="~/R/win-library/3.3")
library("mosaic", lib.loc="~/R/win-library/3.3")
```

###8.31

```{r}
favstats(Pulse ~ Award, data = StudentSurvey)
anova = anova(lm(Pulse ~ Award, StudentSurvey)); anova
p.value = anova$"Pr(>F)"[1]
```
As $n_i \geq 30$ for all i, the std devs are good.

$H_0: \mu_1 = \mu_2 = \mu_3; H_a: \mu_i \neq \mu_j$

The p-value from the ANOVA, $`r p.value`$, is very small. Therefore, we have strong evidence that at least one of the award groups has a mean exercise rate that differs from at least one of the other groups.

###8.32

*(a)*
```{r}
favstats(GillRate ~ Calcium, data = FishGills3)
boxplot(GillRate ~ Calcium, data = FishGills3)
```
As $n_i \geq 30$ for all i, the std devs are good.

*(b)*
```{r}
anova = anova(lm(GillRate ~ Calcium, FishGills3)); anova
p.value = anova$"Pr(>F)"[1]
```
$H_0: \mu_1 = \mu_2 = \mu_3; H_a: \mu_i \neq \mu_j$

As the test is sufficient as mentioned in part *(a)*, we can test to find the ANOVA table. The p-value from the ANOVA, $`r p.value`$, is very small. Therefore, we have strong evidence that at least one of the calcium rates has a gill beat rate that differs from at least one of the other groups.

###8.52


###D.36


###D.37


###D.38

