---
title: "Homework 4"
author: "David Rodden"
date: "March 6, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("Lock5withR", lib.loc="~/R/win-library/3.3")
```

###5.40
```{r}
old.mu = 62; old.sigma = 18
studentA.old_score = 47
studentB.old_score = 90
studentA.z = (studentA.old_score - old.mu)/old.sigma
studentB.z = (studentB.old_score - old.mu)/old.sigma
studentA.z; studentB.z

new.mu = 75; new.sigma = 10
studentA.new_score = new.mu + studentA.z * new.sigma
studentB.new_score = new.mu + studentB.z * new.sigma
studentA.new_score; studentB.new_score
```

The new scores of the students who scored 47 and 90 would earn `r round(studentA.new_score, 2)` and `r round(studentB.new_score, 2)` respectively.

###5.41

```{r}
mean = 45; st_dev = 8

```
*(a)*


###6.24

```{r}
flight.mean = 0.8
flight.stderr = sqrt(0.8*(1-0.8)/400)
```
Since the standard error of the flight equates to being only 0.2, it is not likely that the flights will be within 0.03 of the true population proportion.
Test

###6.48

```{r}
me = 0.3
z.star = qnorm(0.955)
estimate.conservative = 0.5
estimate.first = 0.7
estimate.second = 0.9
size.conservative = ceiling((z.star/me)^2 * estimate.conservative * (1 - estimate.conservative))
size.conservative
size.first = ceiling((z.star/me)^2 * estimate.first * (1 - estimate.first))
size.first
size.second = ceiling((z.star/me)^2 * estimate.second * (1 - estimate.second))
size.second
```
The sample size needed for instances $p = 0.5, 0.7, 0.9$ respectively with $95$% confidence and a margin of error within $\pm3$% are `r size.conservative`, `r size.first`, and `r size.second` respectively.
From the data observed above, we can see that with the elevation of our p estimate, the sample size needed to give decreases.

###6.54

```{r}
icu.status = ICUAdmissions$Status
icu.size = length(icu.status)
p.hat = sum(icu.status %in% 0)/icu.size; p.hat
z.star = qnorm(0.955)
se = sqrt(p.hat * (1 - p.hat)/icu.size); se
ci.lower = round(p.hat - z.star * se, 3)
ci.upper = round(p.hat + z.star * se, 3)
```
The confidence interval for the proportion of ICU patients who live is `r ci.lower` to `r ci.upper`.