---
title: "Statistics Homework 8"
author: "David Rodden"
date: "April 25, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("Lock5withR", lib.loc="~/R/win-library/3.3")
library("mosaic", lib.loc="~/R/win-library/3.3")
```
###9.22
```{r}
xyplot(AvgMercury ~ Alkalinity, data = FloridaLakes, type = c("p", "r"), pch = 16, col = "black")
```
The scatterplot provided by **FloridaLakes** has a departure from linearity. That is, it has a trend that is clearly decreasing, but not in a linear fashion.


###9.26
*(a)*

```{r}
model = lm(WinPct ~ PtsFor, data = NBAStandings)
summary(model)
```

###9.50


###9.64
*(a)*

```{r}
xyplot(Price ~ Size, data = HomesForSaleNY, pch = 16, col = "black", 
       lwd = 2, level = .9, panel=panel.lmbands, band.lty=c(2,3),
       band.col=c("blue","forestgreen"), band.lwd=2)
```
Square footage is an effective predictor of price as 27/30 = 90% of data points are within the green bands.

*(b)*

```{r}
homes = lm(Price ~ Size, data=HomesForSaleNY); homes
homes.2kpe = coef(homes)["(Intercept)"] + 2 * coef(homes)["Size"]; homes.2kpe
```
A point estimate for the price of a 2000-square-foot New York home is $\$`r homes.2kpe * 1000`$.

*(c)*

```{r}
home.confint = predict(homes, as.data.frame(cbind(Size = 2)), interval = "confidence", level = .9)
home.confint
```
The confidence interval for the price of a specific 2000-square foot New York home is `r home.confint[2]` and `r home.confint[3]` respectively.

*(d)*

```{r}
home.predint = predict(homes, as.data.frame(cbind(Size = 2)), interval = "prediction", level = .9)
home.predint
```
The prediction interval for the price of a specific 2000-square-foot New York home is `r home.predint[2]` and `r home.predint[3]` respectively.
