---
title: "Homework 5"
author: "David Rodden"
date: "March 25, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("Lock5withR", lib.loc="~/R/win-library/3.3")
```

###6.188
```{r}
total.male = length(which(ICUAdmissions$Sex == 0))
total.female = length(which(ICUAdmissions$Sex == 1))
dead.male = length(subset(ICUAdmissions, Sex == 0 & Status == 1))
dead.female = length(subset(ICUAdmissions, Sex == 1 & Status == 1))
deadProp.male = dead.male / total.male
deadProp.female = dead.female / total.female
deadProp.difference = deadProp.male - deadProp.female
```
To ensure that the sample size is large enough in each group, we check that $n_1p_1, n_1(1-p_1), n_2p_2, n_2(1 - p_2) \geq 10$.
```{r}
male.test1 = total.male * deadProp.male; male.test1
male.test2 = total.male * (1 - deadProp.male); male.test2
female.test1 = total.female * deadProp.female; female.test1
female.test2 = total.female * (1 - deadProp.female); female.test2
```
Since all are above, 10, we know that the sample size is large enough in each group.
```{r}
deadProp.se = sqrt(
    (deadProp.male * (1 - deadProp.male) / total.male) + 
    (deadProp.female * (1 - deadProp.female) / total.female))
z.star = qnorm(.955)
confidence.lower = deadProp.difference - z.star * deadProp.se; confidence.lower
confidence.upper = deadProp.difference + z.star * deadProp.se; confidence.upper
```

The 95% confidence interval for the difference in the proportion who die between males and females is between `r confidence.lower` and `r confidence.upper`.

###6.204
*(a)*

$H_0: p_t = p_p; H_a: p_t > p_t$
```{r}
size.thc = 79; size.proch = 78
effective.thc = 36; effective.proch = 16
thc.test = prop.test(c(effective.thc, effective.proch), c(size.thc, size.proch),
                     alternative = "greater")
p.value = thc.test$p.value
```
Since the p-value is $`r p.value`$, which is less than 0.01 per the significance level, we reject the null hypothesis in favor of the alternative hypothesis.

*(b)*

It is important that these data come from a well-designed experiment so that the results are clear and so that they cannot be misconstrued.

###6.248

```{r}
total.male = subset(NutritionStudy, Sex == "Male")$Fiber
total.female = subset(NutritionStudy, Sex == "Female")$Fiber
size.male = length(total.male)
size.female = length(total.female)
fiber.male = mean(total.male)
fiber.female = mean(total.female)
fiber.difference = fiber.male - fiber.female
fiber.se = sqrt(
  (sd(total.male)^2/size.male) + 
    (sd(total.female)^2/size.female));fiber.se
fiber.df = if(size.male > size.female)  size.male - 1 else size.female - 1
t.star = qt(.955, fiber.df);t.star
confidence.lower = fiber.difference - t.star * fiber.se
confidence.upper = fiber.difference + t.star * fiber.se
```
The 95% confidence interval for the difference in number of grams of fiber eaten in a day between males and females is between `r confidence.lower` and `r confidence.upper`.
No difference between males and females is a plausible option for the population difference in number of grams of fiber eaten because 0 falls within the 95% confidence interval displayed above.

###2.290

Since the group of students are being used for two different tests, this is paired data.

```{r}
size.total = length(QuizPulse10$Student)
mean.lecture = mean(QuizPulse10$Lecture)
mean.quiz = mean(QuizPulse10$Quiz)
sd.lecture = sd(QuizPulse10$Lecture)
sd.quiz = sd(QuizPulse10$Quiz)
mean.difference = mean.lecture - mean.quiz
sd.difference = sd.lecture - sd.quiz
t.star = qt(.955, size.total - 1)
confidence.lower = mean.difference - t.star * sd.difference / sqrt(size.total)
confidence.upper = mean.difference + t.star * sd.difference / sqrt(size.total)
```
The 95% confidence interval for the difference in mean pulse rate between students in a class lecture and taking a quiz is between `r confidence.lower` and `r confidence.upper`.