---
title: "Homework 5"
author: "David Rodden"
date: "March 25, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("Lock5withR", lib.loc="~/R/win-library/3.3")
```

###6.188
```{r}
total.male = length(which(ICUAdmissions$Sex == 0))
total.female = length(which(ICUAdmissions$Sex == 1))
dead.male = length(subset(ICUAdmissions, Sex == 0 & Status == 1))
dead.female = length(subset(ICUAdmissions, Sex == 1 & Status == 1))
deadProp.male = dead.male / total.male
deadProp.female = dead.female / total.female
deadProp.difference = deadProp.male - deadProp.female
```
To ensure that the sample size is large enough in each group, we check that $n_1p_1, n_1(1-p_1), n_2p_2, n_2(1 - p_2) \geq 10$.
```{r}
male.test1 = total.male * deadProp.male; male.test1
male.test2 = total.male * (1 - deadProp.male); male.test2
female.test1 = total.female * deadProp.female; female.test1
female.test2 = total.female * (1 - deadProp.female); female.test2
```
Since all are above, 10, we know that the sample size is large enough in each group.
```{r}
deadProp.se = sqrt(
    (deadProp.male * (1 - deadProp.male) / total.male) + 
    (deadProp.female * (1 - deadProp.female) / total.female))
z.star = qnorm(.955)
confidence.lower = deadProp.difference - z.star * deadProp.se; confidence.lower
confidence.upper = deadProp.difference + z.star * deadProp.se; confidence.upper
```

The 95% confidence interval for the difference in the proportion who die between males and females is between `r confidence.lower` and `r confidence.upper`.

###6.204
*a*
$H_0: p_t = p_p; H_a: p_t > p_t$
```{r}
size.thc = 79; size.proch = 78
effective.thc = 36; effective.proch = 16
prop.thc = effective.thc / size.thc
prop.proch = effective.proch / size.proch
prop.difference = prop.thc - prop.proch; prop.difference
prop.se = sqrt(
    (prop.thc * (1 - prop.thc) / size.thc) +
      (prop.proch * (1 - prop.proch) / size.proch)
)
z = prop.difference / prop.se; z
p.value = pnorm(1 - z)
```
Since the p-value is `r p.value` and much greater than 0.01, per the significance level, we reject the alternate hypothesis.

*b*


###6.248

```{r}
total.male = subset(NutritionStudy, Sex == "Male")$Fiber
total.female = subset(NutritionStudy, Sex == "Female")$Fiber
size.male = length(total.male)
size.female = length(total.female)
fiber.male = mean(total.male)
fiber.female = mean(total.female)
fiber.difference = fiber.male - fiber.female
fiber.se = sqrt(
  (sd(total.male)^2/size.male) + 
    (sd(total.female)^2/size.female));fiber.se
fiber.df = if(size.male > size.female)  size.male - 1 else size.female - 1
t.star = qt(.955, fiber.df);t.star
confidence.lower = fiber.difference - t.star * fiber.se
confidence.upper = fiber.difference + t.star * fiber.se
```
The 95% confidence interval for the difference in number of grams of fiber eaten in a day between males and females is between `r confidence.lower` and `r confidence.upper`.
No difference between males and females is a plausible option for the population difference in number of grams of fiber eaten because 0 falls within the 95% confidence interval displayed above.
