---
title: "Statistics Homework 6"
author: "David Rodden"
date: "April 9, 2017"
output: pdf_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
library("Lock5withR", lib.loc="~/R/win-library/3.3")
library("mosaic", lib.loc="~/R/win-library/3.3")
```

###7.25

$H_0: p_1=0.301, p_2=0.176, p_3=0.125, p_4=0.097, p_5=0.079, p_6=0.067, p_7=0.058, p_8=0.051, p_9=0.046$
$H_{a}:$ At least one of the proportions is different from Benford's law
```{r}
xt = xchisq.test(Benford$Address, p = Benford$BenfordP)
p.value = xt$p.value; p.value
xsq = xt$statistic; xsq
df = xt$parameter; df
```
We find that the p-value $\approx$ `r p.value` using the upper tail beyond `r xsq` of a chi-square distribution with `r df` degrees of freedom.
This is not a small p-value, so we do not have enough evidence that the first digits of street addresses in a phone book do not follow Benford's law.

###7.26

$H_0: p_1=0.301, p_2=0.176, p_3=0.125, p_4=0.097, p_5=0.079, p_6=0.067, p_7=0.058, p_8=0.051, p_9=0.046$
$H_{a}:$ At least one of the proportions is different from Benford's law
```{r}
xt = xchisq.test(Benford$Invoices, p = Benford$BenfordP)
p.value = xt$p.value; p.value
xsq = xt$statistic; xsq
df = xt$parameter; df
```
We find that the p-value $\approx `r p.value`$ using the upper tail beyond `r xsq` of a chi-square distribution with `r df` degrees of freedom.
This is a very small p-value, so we have enough evidence that the first digit of invoices do not follow Benford's law.

###7.29

$H_0: p_0 = p_1 = p_2 = p_3 = ... = p_8 = p_9 = 0.10$

$H_{a}:$ Some $p_i \neq 0.10$
```{r}
xt = xchisq.test(table(Digits$SSN8))
p.value = xt$p.value; p.value
xsq = xt$statistic; xsq
df = xt$parameter; df
```
We find that the p-value $\approx `r p.value`$ using the upper tail beyond `r xsq` of a chi-square distribution with `r df` degrees of freedom. This is very large, so, we have no substantial evidence that the eighth digits of SSN are not random.

###7.42


###7.54