---
title: "Statistics Homework 7"
author: "David Rodden"
date: "April 20, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("Lock5withR", lib.loc="~/R/win-library/3.3")
library("mosaic", lib.loc="~/R/win-library/3.3")
```

###8.31

```{r}
favstats(Pulse ~ Award, data = StudentSurvey)
anova = anova(lm(Pulse ~ Award, StudentSurvey)); anova
p.value = anova$"Pr(>F)"[1]
```
As $n_i \geq 30$ for all i, the std devs are good.

$H_0: \mu_1 = \mu_2 = \mu_3; H_a: \mu_i \neq \mu_j$

The p-value from the ANOVA, $`r p.value`$, is very small. Therefore, we have strong evidence that at least one of the award groups has a mean exercise rate that differs from at least one of the other groups.

###8.32

*(a)*
```{r}
verify = favstats(GillRate ~ Calcium, data = FishGills3); verify
boxplot(GillRate ~ Calcium, data = FishGills3)
```
As $n_i \geq 30$ for all i, the std devs are good.

*(b)*
```{r}
anova = anova(lm(GillRate ~ Calcium, FishGills3)); anova
p.value = anova$"Pr(>F)"[1]
```
$H_0: \mu_1 = \mu_2 = \mu_3; H_a: \mu_i \neq \mu_j$

As the test is sufficient as mentioned in part *(a)*, we can test to find the ANOVA table. The p-value from the ANOVA, $`r p.value`$, is very small. Therefore, we have strong evidence that at least one of the calcium rates has a gill beat rate that differs from at least one of the other groups.

###8.52


```{r}
mean(GillRate ~ Calcium, data = FishGills3)
tukey = TukeyHSD(lm(GillRate ~ Calcium, data = FishGills3)); tukey
```
In **8.32**, the ANOVA table indicated that the mean gill rates differed due to the calcium levels. We can see that High and Medium calicum means are very close to one another, the difference in means being only `r tukey$Calcium[2]`. However, the difference between low & medium and low & high are quite different, `r tukey$Calcium[1]` and `r tukey$Calcium[3]` respectively. So, it is evident that low calcium levels lead to a drastically different mean.

###D.36


###D.37


###D.38

